\chapter{Cost estimation}

After finalizing the design of the vacuum chamber and vacuum system, a cost estimation can be made. This estimation is essential for budgeting the entire project and for securing adequate funding.\\

\noindent Most components of the vacuum chamber can be purchased off the shelf. Table \ref{tab:vacuum_cost} below lists estimated costs for various parts of the vacuum system, along with an estimated quantity $N$ for each required part.
The prices above are based on prices on the website of Pfeiffer Vacuum \cite{pfeiffervacuum}. To see the prices one has to make an account. The prices of the devices above are estimations and depend on their configuration.


\begin{table}[H]
    \centering
    \caption{Overview of the estimated costs for different parts of the vacuum system.}
    \begin{tabular}{
        >{\raggedright\arraybackslash}p{5cm}
        >{\raggedright\arraybackslash}p{1.5cm}
        S[table-format=6.2]
        >{\raggedright\arraybackslash}p{5cm}
        }
        \toprule
        \textbf{Part}                                          & \textbf{N} & \textbf{Price / Part (€)} & \textbf{Type}            \\
        \midrule
        ATH3204 MT                                             & 1          & 54000.00                  & Turbo Molecular Pump     \\
        ACP90                                                  & 1          & 16200.00                  & Backing Pump             \\
        ITR 90                                                 & 1          & 1120.00                   & Manometer                \\
        PrismaPro\textsuperscript{\textregistered}             & 1          & 11100.00                  & Mass Spectrometer        \\
        Venting valve, manually actuated, stainless steel      & 1          & 94.50                     & Venting Valve            \\
        Weld-on flange ring, stainless steel                   & 1          & 345.00                    & Weld-on Flange Ring      \\
        Weld-on flange, rotatable, stainless steel             & 1          & 29.60                     & Welding Flange           \\
        Weld-on flange, rotatable with thread, stainless steel & 1          & 25.60                     & Rotatable Welding Flange \\

        %        \textbf{Total:}                                        &            & 83914.70                                             \\
        \bottomrule
    \end{tabular}
    \label{tab:vacuum_cost}
\end{table}




The total estimated costs in table \ref{tab:vacuum_cost} amount to $83,914.70$ €. However, this cost estimation is not complete.
For instance, the cost of the vacuum chamber itself remains unknown and cannot be estimated at this stage. The manufacturer does not provide list prices for such custom-made items and would only provide a cost estimate upon specific order inquiry.
It is anticipated that the vacuum chamber itself would represent one of the largest expenses for the entire project, primarily due to the necessity of custom manufacturing.\\
Furthermore, the final number and types of ports, as well as other components such as windows, gas inlets, feedthroughs, and coaxials, have not been finalized or included in the cost estimation yet.
For a complete list of the components and their approximate prices, different companies such as Pfeiffer Vacuum, Streicher Machinery, Leybold, or Edwards Vacuum (just as examples, no affiliation) could be contacted. However, as mentioned before, the exact costs will highly depend on the very final design of the vacuum system, and manufacturers are often not able to list those upon order and being provided with a fixed design. In correspondence with Streicher Machinery, only the designing of the vacuum chamber would amount to around 3000 €.\\

The costs can be lowered by using older vacuum systems, which are or have already been in use in different laboratories at universities, and manufacturing some parts in-house.\\


\section{Outlook}

In the future, the costs of the whole vacuum system could be more exactly approximated by sending the design to vacuum chamber manufacturers and receiving their quotas. 
For this, the design shall be finalized, since without a finished system extra costs for the design might arise ($\approx$ 3000 € as stated before), and companies do not provide cost estimates without a realistic chance of receiving an order.
All costs can be lowered by incorporating the vacuum system in an already existing system, and utilizing older, used, or gifted components. 
Some flanges and metal pieces might be manufactured by the university's workshop, which can further lower the costs for specialized small parts. 





%ATH3204 MT (TMP): 54000 €\\
%ACP90 (backing pump): 16200 €\\
%ITR 90 (manometer) : 1120 €\\
%PrismaPro$\textsuperscript{\textregistered}$ (mass spectrometer): 11100 €\\
%Venting valve, manually actuated, stainless steel, DN 10 ISO-KF = 94.50 €\\
%Anschweißflanschring, Edelstahl 1.4301/304, DN 320 ISO-K = 345 €\\
%Anschweißflansch, drehbar mit Gewinde, Edelstahl 304L, DN 25 CF = 29.60 €\\
%Anschweißflansch, drehbar mit Gewinde, Edelstahl 304L, DN 40 CF = 25.60 €\\


%\cvici{include some text and explanation, Why do we only know the costs of these components? why do we not know the costs of the entire vacuum chamber?}
%\todo{Quantities}

%\todo{include gas inlet, feedthrough, coaxial, window}

\begin{table}[H]
    \centering
    \caption{Overview of the estimated costs for different parts of the vacuum system.}
    \begin{tabular}{
        >{\raggedright\arraybackslash}p{5cm}
        >{\raggedright\arraybackslash}p{0.1cm}
        S[table-format=6.2]
        >{\raggedright\arraybackslash}p{5cm}
        }
        \toprule
        \textbf{Part}                                          & & \textbf{Price / Part (€)} & \textbf{Type}            \\
        \midrule
        ATH3204 MT                                             &           & 54000.00                  & Turbo Molecular Pump     \\
        ACP90                                                  &           & 16200.00                  & Backing Pump             \\
        ITR 90                                                 &           & 1120.00                   & Manometer                \\
        PrismaPro\textsuperscript{\textregistered}             &           & 11100.00                  & Mass Spectrometer        \\
        Venting valve, manually actuated, stainless steel      &           & 94.50                     & Venting Valve            \\
        Weld-on flange ring, stainless steel                   &           & 345.00                    & Weld-on Flange Ring      \\
        Weld-on flange, rotatable, stainless steel             &           & 29.60                     & Welding Flange           \\
        Weld-on flange, rotatable with thread, stainless steel &           & 25.60                     & Rotatable Welding Flange \\

        %        \textbf{Total:}                                        &            & 83914.70                                             \\
        \bottomrule
    \end{tabular}
    \label{tab:vacuum_cost}
\end{table}
