\section*{Introduction}

As part of the course ''Fusion Reactor Design'' held at \emph{TU Graz} and \emph{TU Munich}
students have to design a table top fusion stellarator.
This report focus on the design of the vacuum and the vacuum vessel.
This includes the main recipient, the ports and the vacuum pumps.
The report is divided into four primary sections: Vacuum Chamber Design, Vacuum Design, Radiation Protection and Cost Estimation.

In the first section, we delve into the design of the vacuum chamber, detailing its structure, components, and the various ports and feedthroughs incorporated for different purposes, explaining their specific roles.
The Vacuum Design section is dedicated to achieving Ultra High Vacuum (UHV) conditions using a turbomolecular pump, and it also addresses the challenges of insulation and outgassing.
The following section addresses the critical aspect of radiation protection, considering the various types of radiation emitted from the plasma and the design of the radiation shield.
The final section, Cost Estimation, provides a detailed breakdown of the costs associated with the design and implementation of the fusion reactor.
But it should be noted that not all the costs, especially the price of the the entire vacuum chamber is not included, as most of the components are not commercially available and have to be custom made.

This report is a collaborative effort by a team, each contributing their expertise to different sections of the report and also provides an overview of the ports required by each team involved in the design process, including the vacuum team, coil team, design team, diagnostic team, and heating team.

The goal of this report is to provide a detailed description of the vacuum system and rough cost estimation for the vacuum system.

